Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex
Fix a couple of clumsy phrasings.

We evaluated the Moose benchmarks using the reference Mark-Compact and Mark-Sweep algorithms and by analysing the wildfly code base\footnote{http://www.wildfly.org/}. We distinguish four configurations:
\begin{itemize}
\item \emph{Sweep}: VM with standard GC parameters and the Mark-Sweep algorithm.
\item \emph{Compact}: VM with standard GC parameters and the Mark-Compact algorithm.
\item \emph{Compact-16}: VM with standard GC parameters, except Eden size which is 16 times larger, and the Mark-Compact algorithm.
\item \emph{Sweep-16}: VM with standard GC parameters, except Eden size which is 16 times larger, and the Mark-Sweep algorithm.
\end{itemize}
With a larger Eden, more overall memory is used (in our case 90 extra Mb are used), but scavenge time is expected to be lower. Indeed, the scavenger is an implementation of Ungar's scavenger~\cite{Scavenger} and the scavenge time is proportional to the number of surviving objects.
%To evaluate the performance, we use:
%\begin{itemize}
%	\item the production VM generated by the CI of opensmalltalk-vm\footnote{https://github.com/OpenSmalltalk/opensmalltalk-vm}, that we call Mark-Compact or Compact.
%	\item a custom compiled VM, which features a different compactor, that we call Mark-Sweep or Sweep.
%\end{itemize}

@@

\paragraph{ExpandProperties.} The ExpandProperties benchmark grows the memory by around 1 Gb. Compaction time is a little bit better with the sweep algorithm as for the previous benchmark, but execution time is much worse. We believe this is due to worse locality of objects. With a larger Eden, the scavenge time is much smaller and the execution time is a bit faster due to improved object locality.

>>>>

We evaluated the Moose benchmarks using the reference Mark-Compact and Mark-Sweep algorithms and by analysing the wildfly code base\footnote{http://www.wildfly.org/}. We distinguish four configurations:
\begin{itemize}
\item \emph{Sweep}: VM with standard GC parameters and the Mark-Sweep algorithm.
\item \emph{Compact}: VM with standard GC parameters and the Mark-Compact algorithm.
\item \emph{Compact-16}: VM with standard GC parameters, except Eden size which is 16 times larger, and the Mark-Compact algorithm.
\item \emph{Sweep-16}: VM with standard GC parameters, except Eden size which is 16 times larger, and the Mark-Sweep algorithm.
\end{itemize}
With a larger Eden, more overall memory is used (in our case an extra 90 Mb), but scavenge time is expected to be lower. The Spur scavenger is an extended implementation of Ungar's classic generation scavenger~\cite{Scavenger} and the scavenge time is proportional to the number of surviving objects.
%To evaluate the performance, we use:
%\begin{itemize}
%	\item the production VM generated by the CI of opensmalltalk-vm\footnote{https://github.com/OpenSmalltalk/opensmalltalk-vm}, that we call Mark-Compact or Compact.
%	\item a custom compiled VM, which features a different compactor, that we call Mark-Sweep or Sweep.
%\end{itemize}

@@

\paragraph{ExpandProperties.} The ExpandProperties benchmark grows the memory by around 1 Gb. Compaction time is a little bit better with the sweep algorithm as for the previous benchmark, but execution time is much worse. We believe this is due to worse locality of objects. With a larger Eden,  scavenge time is much smaller and the execution time is a bit faster due to improved object locality.
